---
title: "Creating Mock Data for VueForAll - IG Cup 2022"
author: "Annabel Wing-Yan Fan"
date: "1/21/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# import necessary libraries
library(tidyverse)

# load data
videogame.df <- read.csv("videogames.csv") #read_csv() is better but isn't working for some reason
videogame.df$Genre <- gsub(",.*","",videogame.df$Genre)

# define functions here
generate_Sex <- function(n) {
  Sexes = c("Man", "Woman")
  probabilities = c(0.51219512195122, 0.48780487804878)
  Sex <- sample(Sexes, size=n, replace=TRUE, prob=probabilities)
  return(Sex)
}

generate_Gender <- function(n) {
  Genders = c("Male", "Female", "NonBinary", "Other") # can use to calculate cisGender, transGender
  probabilities = c(0.40, 0.30, 0.20, 0.10)
  Gender <- sample(Genders, size=n, replace=TRUE, prob=probabilities)
  return(Gender)
}

generate_Ethnicity <- function(n) {
  ethnicities = c("Indigenous Peoples", "Asian", "Black or African American", "Hispanic or Latino", "Native Hawaiian or Other Pacific Islander", "White")
  Ethnicity <- sample(ethnicities, size=n, replace=TRUE)
  return(Ethnicity)
}

generate_console <- function(n) {
  #platforms = c("PC", "Console", "Handheld", "Mobile")
  consoles = videogame.df$Console
  console <- sample(consoles, size=n, replace=TRUE)
  return(console)
}

generate_game <- function(n) {
  games = videogame.df$Title
  game <- sample(games, size=n, replace=TRUE)
  return(game)
}

generate_genre <- function(n) {
  #genres = c("Sandbox", "RTS", "FPS and TPS", "MOBA", "RPG", "Simulation", "Sport", "Puzzle", "Strategy", "Survival", "Party", "Platformer", "Metroidvania", "Rhythm")
  genres = unique(videogame.df$Genre)
  genre <- sample(genres, size=n, replace=TRUE)
  return(genre)
}

# takes an array of Sex
generate_colouranomaly <- function(Sex) {
  colouranomalies = c("Protan-A", "Deuter-A", "Tritan-A", "Protan", "Deuter", "Tritan", "Mono", "Norm")
  ca = empty_vec <- rep(NA, length(Sex))
  
  for (iSex in 1:length(Sex)) {
    # determine probability based on Sex 
    if (Sex[iSex] == "Male") {
    # Anomalous Trichromacy: protanomaly (1.3%), deuteranomaly (5.0%), tritanomaly (0.0001%)
    # Dichromacy: protanopia (1.3%), deuteranopia (1.2%), tritanopia (0.001%)
    # Rod Monochromacy: 0.00001%
    #probabilities = c(1.3/100, 5/100, 0.0001/100, 1.3/100, 1.2/100, 0.001/100, 0.00001/100, 0.913)
      
    # exaggerated 
      probabilities = c(0.1, 0.3, 0.2, 0.08, 0.01, 0.01, 0.0001, 0.2999)
  } else  {
    # protanomaly (0.02%), deuteranomaly (0.35%), tritanomaly (0.0001%)
    # Dichromacy: protanopia (0.02%), deuteranopia (0.01%), tritanopia (0.03%)
    # Rod Monochromacy: 0.00001%
    #probabilities = c(0.02/100, 0.35/100, 0.0001/100, 0.02/100, 0.01/100, 0.03/100, 0.00001/100, 0.996)
    # exaggerated 
      probabilities = c(0.05, 0.2, 0.05, 0.08, 0.01, 0.01, 0.0001, 0.5999)
  }
  
  # sample from colour anomalies and add to vector
  ca[iSex] <- sample(colouranomalies, size=1, replace=TRUE, prob=probabilities)
    
  }
  
  return(ca)
}

```

# Gamer Profile

We want to create some mock data that would otherwise be gathered from questionnaires and vision assessments on the VueForAll WebApp.

The data will consist of:
- Demographic info: Age, Sex, Gender, Ethnicity
- Gamer info: HoursPlayedWeekly, MostUsedPlatform,	FavouriteGame,	FavouriteGenre
- Vision: ColourAnomaly, ColourAnomalyStrength

```{r}
# check if data already exists
if (file.exists("gamerProfile-data.csv")){
  print("file already exists")
} else {
  # create the data
  N = 5000
  
  col_names <- c("Age", "Sex", "Gender", "Ethnicity", "HoursPlayedWeekly", "MostUsedPlatform", "FavouriteGame", "FavouriteGenre", "ColourAnomaly", "ColourAnomalyStrength")
  
  data <- data.frame(matrix(ncol = length(col_names), nrow = N)) 
  colnames(data) <- col_names
  
  # this is a bit of lazy coding, but I don't know how to make it more efficient
  data$Age <-  sample(10:60, N, replace=TRUE) 
  data$Sex <- generate_Sex(N)
  data$Gender <- generate_Gender(N)
  data$Ethnicity <- generate_Ethnicity(N)
  
  data$HoursPlayedWeekly <- rnorm(N, mean=8, sd=3) 
  data$HoursPlayedWeekly <- ceiling(data$HoursPlayedWeekly)
  data$MostUsedPlatform <- generate_console(N)
  data$FavouriteGame <- generate_game(N) # grab a random game from the list of games
  #data$FavouriteGenre <- generate_genre(N)
  data$FavouriteGenre <- videogame.df$Genre[match(data$FavouriteGame,videogame.df$Title)] # find genre of favorite game
  
  data$ColourAnomaly <- generate_colouranomaly(data$Sex)
  data$ColourAnomalyStrength <- sample(c("weak", "med", "strong"), N, replace = TRUE) # randomly assign strength
  data$ColourAnomalyStrength[!endsWith(data$ColourAnomaly, 'A')] <- "colourblind"
  data$ColourAnomalyStrength[data$ColourAnomaly == "Norm"] <- NA
  
}

write.csv(data, "gamerProfile-data.csv")

```


```{r analysis}
# make sure everything is in the correct data type
data <- data %>% 
  mutate(Sex = factor(Sex),
         Gender = factor(Gender),
         Ethnicity = factor(Ethnicity),
         MostUsedPlatform = factor(MostUsedPlatform),
         FavouriteGenre = factor(FavouriteGenre),
         ColourAnomaly = factor(ColourAnomaly),
         ColourAnomalyStrength = factor(ColourAnomalyStrength)
         )

table(data$ColourAnomaly)

```

# Game Settings Data

```{r}
# create a dataset with video games and (simulated) settings
# 0 = No; 1 = Limited; 2 = Full
settings.df <- videogame.df %>% select(Title)
settings.df$colourblindmode <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE, prob=c(0.5,0.2,0.3))
settings.df$brightness <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$gamma <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$uiSize <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$motionblur <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$camerashake <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$cameraSpeed <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$fieldofview <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$settings <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$photosensitivity <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$visualInfoComplexity <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$moveInvert <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$sensitiveContentFilter <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$gameSpeed <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)
settings.df$textSpeed <- sample(c(0,1,2), size=nrow(videogame.df), replace=TRUE)

write.csv(data, "gameSettings-data.csv")
```

N